---
title: "W9_Stock_Analysis"
author: "Daniel Van Gorkum"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
format: html
editor: visual
execute:
  echo: true
  warning: false
  message: false
  keep-md: true
---

## 

```{r}
# Ensure required packages are installed
packages <- c("tidyverse", "tidyquant", "dygraphs", "timetk", "quantmod")
installed <- packages %in% rownames(installed.packages())
if(any(!installed)) install.packages(packages[!installed], dependencies = TRUE)

# Load libraries
library(tidyverse)
library(tidyquant)
library(dygraphs)
library(timetk)
library(quantmod)
```

```{r}
# Replace this vector with whatever tickers your friend gives you at meeting time

my_stocks <- c("AAPL", "GOOG", "NVDA", "TSLA", "KO")

stock_data <- tq_get(my_stocks, from = Sys.Date() - years(5))
glimpse(stock_data)

```

```{r}
stock_returns <- stock_data %>%
group_by(symbol) %>%
tq_transmute(select = adjusted,
mutate_fun = periodReturn,
period = "daily",
col_rename = "daily_return")
# Convert to wide format

returns_wide <- stock_returns %>%
pivot_wider(names_from = symbol, values_from = daily_return)

# Use timetk to convert tidy data → xts

returns_xts <- tk_xts(returns_wide, date_var = date)

```

```{r}
dygraph(returns_xts, main = "Daily Stock Returns (Last 5 Years)") %>%
dyRangeSelector() %>%
dyLegend(show = "always", hideOnMouseOut = FALSE) %>%
dyOptions(colors = RColorBrewer::brewer.pal(n = length(my_stocks), name = "Set1"))

```

```{r}
portfolio_returns <- stock_returns %>%
tq_portfolio(assets_col = symbol,
returns_col = daily_return,
weights = NULL, # equally weighted
col_rename = "portfolio_return")

portfolio_xts <- tk_xts(portfolio_returns, date_var = date)

dygraph(cumprod(1 + portfolio_xts),
main = "Equally Weighted Portfolio Growth") %>%
dyRangeSelector()

```

# Summary

What I have seen through the data and the visuals is that an individual stock by themselves is very volatile as can impose a lot of risk for an individual who puts all their eggs in one basket. However if we equally disburse to all the 5 different equities and make one portfolio, you get a relatively safe return with less volatility (lower standard deviation), especially if you are looking for holding in the long-term at a bullish projection.
